Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Added comment to code
Discuss with Ali code from line 234 as this will apply to multiple geographies, may be a way to do it more efficiently.

The following code is to compare mortality rates per one, by age groups of 5 and sex for England and England.

ALSO PART OF THE BELOW CODE WILL BE NEEDED FOR THE MSLT AND DISMOD COLLECTION. GENERATE DATA INPUTS FOR DISMOD II FROM HERE.

@@

##Create age categories index in GBDdata (rounding mid age)

@@

##Convert variable val to numberic

@@

##Filter data for England and Greater London adn generate per person rates (per 100,000 in original data)
#England
GBDEngland <- filter(GBDdata, location == "england" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)

>>>>

The following code serves to sort out the GBD data to the inputs required for the life table, disease life table and Dismod II

ALSO PART OF THE BELOW CODE WILL BE NEEDED FOR THE MSLT AND DISMOD COLLECTION. GENERATE DATA INPUTS FOR DISMOD II FROM HERE. These data should be used to generate the general life table and disease life tables (Figure 3).

@@

##Create age categories index in GBDdata (rounding mid age), total of 20 age groups. These are the age cohorts to simulate.

@@

##Create age and sex categories to obtain population numbers. Population numbers from GBD are used in 
##Dismod II. For the Life table (Figure 3), the numbers may be from the synthetic population.

GBDdata$sex_age_cat <- paste(GBDdata$age_cat,GBDdata$sex, sep = "_"  )

##Convert variable "val" to numeric as its latter used in calculations.

@@

##Generate population numbers for England and Greater London in a new data frame ("GBD_population") and then separate in dataframes for England and Greater London (this avoids repeating the same code).

GBD_population <- filter(GBDdata, measure == "deaths", cause == "all causes", metric == "rate" | metric == "number" ) %>% select(metric, age_cat, val, sex_age_cat, location)

###Generate population numbers from given number of cases and rates per 100,000 people. 
 for (i in 1:nrow(GBD_population)) {
    if (GBD_population$metric[i] == "number") {
      GBD_population$val_pop[i] <- GBD_population$val[i] * 100000/ GBD_population$val[i + 2]}
   else {GBD_population$val_pop[i] <- NA}
 }
##Remove rows with zero
GBD_population <- GBD_population[!is.na(GBD_population$val_pop),]

##Keep relevant variables

GBD_population <- filter(GBD_population) %>% select(sex_age_cat, val_pop, location)

##Create data frames for Greater London and England population

GBD_population_GL <-  filter(GBD_population, location == "greater london") %>% select(sex_age_cat, val_pop, location)

GBD_population_England <-  filter(GBD_population, location == "england") %>% select(sex_age_cat, val_pop, location)

##Check population total numbers

GreaterLondon <- sum(GBD_population_GL$val_pop)
England <- sum(GBD_population_England$val_pop)

##Generate data frames for England and Grater London with per person rates (per 100,000 in original data).

#England
GBDEngland <- filter(GBDdata, location == "england" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)
